---
title: "Minimal tracked learnr tutorial"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "A minimal learnr tutorial showing explicit learnrTrackR tracking in gradethis check chunks."
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(learnrTrackR)
library(dplyr)
library(tibble)

gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)

tutorial_id <- "minimal_learnr"
student_id <- Sys.getenv("LEARNRTRACKR_STUDENT_ID", unset = "student_demo")
tracking_db_path <- Sys.getenv(
  "LEARNRTRACKR_DB",
  unset = file.path(tempdir(), "learnrtrackr-minimal.sqlite")
)

open_tracking_db <- function() {
  learnrTrackR::init_tracking_db(tracking_db_path, overwrite = FALSE)
}

quebec_temperatures <- tibble::tibble(
  station = c("Québec", "Québec", "Québec", "Montréal", "Montréal", "Montréal"),
  day = as.Date(c(
    "2026-01-01", "2026-01-02", "2026-01-03",
    "2026-01-01", "2026-01-02", "2026-01-03"
  )),
  temp_c = c(-9, -6, -8, -5, -3, -7)
)
```

## Identification

For this prototype, the learner is identified by the environment variable
`LEARNRTRACKR_STUDENT_ID`.

```{r show-student}
tibble::tibble(
  student_id = student_id,
  tutorial_id = tutorial_id,
  tracking_db_path = tracking_db_path
)
```

## Question 1

This multiple-choice question is included as a target use case. In this minimal
prototype, it is not tracked because the current helper is called from
`gradethis::grade_this()` check chunks.

```{r q1_multiple_choice, echo=FALSE}
learnr::question(
  "What is the mean of 2, 4, and 6?",
  learnr::answer("3"),
  learnr::answer("4", correct = TRUE),
  learnr::answer("6"),
  allow_retry = TRUE,
  correct = "Correct.",
  incorrect = "Try again. Add the three values and divide by 3."
)
```

## Question 2

Use `mean()` to compute the mean temperature in the small data set.

```{r show-data}
quebec_temperatures
```

```{r q2_mean_temperature, exercise=TRUE}
mean(quebec_temperatures$temp_c)
```

```{r q2_mean_temperature-solution}
mean(quebec_temperatures$temp_c)
```

```{r q2_mean_temperature-check}
gradethis::grade_this({
  expected <- mean(quebec_temperatures$temp_c)
  correct <- isTRUE(all.equal(.result, expected))
  feedback <- if (correct) {
    "Correct. This is the mean of the temperature column."
  } else {
    "Try again. Use mean() on quebec_temperatures$temp_c."
  }

  con <- open_tracking_db()
  on.exit(DBI::dbDisconnect(con), add = TRUE)

  learnrTrackR::track_gradethis_attempt(
    con = con,
    student_id = student_id,
    tutorial_id = tutorial_id,
    question_id = "q2_mean_temperature",
    submitted_answer = .user_code,
    correct = correct,
    feedback = feedback,
    max_score = 1
  )
})
```

## Question 3

Use `dplyr::summarise()` to compute the mean temperature by station. The result
should contain the variables `station` and `mean_temp_c`.

```{r q3_summarise_temperature, exercise=TRUE}
quebec_temperatures |>
  group_by(station) |>
  summarise(mean_temp_c = mean(temp_c), .groups = "drop")
```

```{r q3_summarise_temperature-solution}
quebec_temperatures |>
  group_by(station) |>
  summarise(mean_temp_c = mean(temp_c), .groups = "drop")
```

```{r q3_summarise_temperature-check}
gradethis::grade_this({
  expected <- quebec_temperatures |>
    dplyr::group_by(station) |>
    dplyr::summarise(mean_temp_c = mean(temp_c), .groups = "drop") |>
    dplyr::arrange(station)

  candidate <- tryCatch(
    {
      .result |>
        as.data.frame() |>
        dplyr::arrange(station)
    },
    error = function(cnd) NULL
  )

  correct <- !is.null(candidate) &&
    all(c("station", "mean_temp_c") %in% names(candidate)) &&
    nrow(candidate) == nrow(expected) &&
    isTRUE(all.equal(candidate$mean_temp_c, expected$mean_temp_c))

  feedback <- if (correct) {
    "Correct. The summary has the expected mean temperature by station."
  } else {
    "Try again. Group by station, then summarise mean_temp_c = mean(temp_c)."
  }

  con <- open_tracking_db()
  on.exit(DBI::dbDisconnect(con), add = TRUE)

  learnrTrackR::track_gradethis_attempt(
    con = con,
    student_id = student_id,
    tutorial_id = tutorial_id,
    question_id = "q3_summarise_temperature",
    submitted_answer = .user_code,
    correct = correct,
    feedback = feedback,
    max_score = 1
  )
})
```

## Results

After submitting the code exercises, run `inspect-results.R` from this example
directory to inspect the stored attempts and scores.
