---
title: "Exporting grades to Canvas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exporting grades to Canvas}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Scope

This guide shows how to prepare a Canvas Gradebook-style CSV grade file from
`learnrTrackR`. The package does not call the Canvas API. The workflow is a
manual CSV import into the Canvas Gradebook.

Instructure's Canvas Instructor Guide states that Gradebook CSV uploads can
update existing assignment grades or create new assignments, but they cannot
update other Gradebook areas such as assignment status, comments, or grade
posting policies.

# Create a small gradebook

```{r setup}
library(learnrTrackR)

db_path <- tempfile(fileext = ".sqlite")
con <- init_tracking_db(db_path, overwrite = TRUE)

register_students(
  con,
  data.frame(
    student_id = c("student_001", "student_002"),
    student_label = c("Student 1", "Student 2"),
    email = c("student.001@example.test", "student.002@example.test"),
    group_id = c("A", "A")
  )
)

register_questions(
  con,
  tutorial_id = "module_01",
  questions = data.frame(
    question_id = c("q1", "q2"),
    max_score = c(1, 1)
  )
)

track_attempt(
  con,
  student_id = "student_001",
  tutorial_id = "module_01",
  question_id = "q1",
  submitted_answer = "mean(x)",
  score = 1,
  max_score = 1,
  require_registered_student = TRUE
)

track_attempt(
  con,
  student_id = "student_002",
  tutorial_id = "module_01",
  question_id = "q1",
  submitted_answer = "sd(x)",
  score = 0,
  max_score = 1,
  require_registered_student = TRUE
)
```

# Build the Canvas table

`canvas_grades()` returns a wide table with the standard leading columns used
in Canvas Gradebook CSV files and one assignment grade column.

```{r canvas-table}
canvas_grades(
  con,
  tutorial_id = "module_01",
  assignment = "Module 01 quiz"
)
```

By default, `learnrTrackR` writes `student_id` values to the `SIS User ID`
column. If your Canvas course matches users with another field, change the
identifier mapping.

```{r login-id}
canvas_grades(
  con,
  tutorial_id = "module_01",
  assignment = "Module 01 quiz",
  student_id_column = "SIS Login ID",
  student_id_source = "email"
)
```

The default grade value is the raw `score`, because Canvas assignment imports
are interpreted as assignment points. If the Canvas assignment is intended to
receive a 0 to 100 value, use `grade_value = "percent"`.

```{r percent}
canvas_grades(
  con,
  tutorial_id = "module_01",
  assignment = "Module 01 percent",
  grade_value = "percent"
)
```

# Export the CSV file

```{r export}
csv_path <- tempfile(fileext = ".csv")

export_canvas_grades(
  con,
  path = csv_path,
  tutorial_id = "module_01",
  assignment = "Module 01 quiz",
  grade_value = "score",
  digits = 2
)

readr::read_csv(csv_path, show_col_types = FALSE)
```

If the database contains several registered groups, use `group_id` to export
only one cohort:

```{r group-export}
canvas_grades(
  con,
  tutorial_id = "module_01",
  assignment = "Module 01 quiz",
  group_id = "A"
)
```

# Suggested Canvas import workflow

Before importing into a real course:

1. Export the current Canvas Gradebook first.
2. Compare the Canvas identifier columns with the `learnrTrackR` export.
3. Confirm whether your course uses `ID`, `SIS User ID`, or `SIS Login ID`.
4. Create the Canvas assignment first when possible, especially when grading
   periods are enabled.
5. Generate a `learnrTrackR` CSV with the matching identifier column.
6. Import the CSV in Canvas's Gradebook import interface.
7. Review the Canvas import preview before saving changes.
8. Validate the workflow on a small test group before importing a full cohort.

# Privacy check before import

The Canvas grade CSV should contain only the identifiers needed for matching,
the section when operationally useful, and the assignment grade column. Do not
include attempts, feedback, free-text answers, or pseudonymisation keys in a
Canvas import file.

```{r disconnect, include = FALSE}
DBI::dbDisconnect(con)
```

# References

- Instructure. Accessed 2026-06-08. How do I import grades in the Gradebook?
  <https://community.canvaslms.com/t5/Instructor-Guide/How-do-I-import-grades-in-the-Gradebook/ta-p/807>
- Instructure. Accessed 2026-06-08. How do I export grades in the Gradebook?
  <https://community.canvaslms.com/t5/Instructor-Guide/How-do-I-export-grades-in-the-Gradebook/ta-p/809>
