---
title: "Course pilot workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Course pilot workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Scope

This vignette introduces the course pilot example included with
`learnrTrackR`. The pilot is a simulated descriptive statistics tutorial with
tracked `learnr` questions, tracked `gradethis` code exercises, CSV and YAML
configuration files, explicit student and teacher launch scripts, and teacher
outputs.

The data are simulated. They are intended only for testing the tracking
workflow.

# Locate the example

```{r locate-example}
library(learnrTrackR)

example_dir <- system.file("examples/course-pilot", package = "learnrTrackR")
example_dir
```

The directory contains:

```{r list-example}
list.files(example_dir)
```

# Read the configuration

```{r read-config}
config_dir <- file.path(example_dir, "config-csv")
yaml_config <- file.path(example_dir, "config", "tracking.yml")
config <- read_tracking_config(config_dir)
yaml_config_data <- read_tracking_config(yaml_config)

config$courses
config$tutorials
config$students
config$questions
yaml_config_data$tutorials
```

# Launch with scripts

For a student-style launch from the example directory:

```{sh run-student, eval = FALSE}
cp student.env.example student.env
Rscript run-student.R
```

For teacher outputs:

```{sh run-teacher, eval = FALSE}
cp teacher.env.example teacher.env
Rscript run-teacher.R
```

# Launch the tutorial locally

The tutorial itself is not launched during vignette rendering. To run it
locally:

```{r run-tutorial, eval = FALSE}
Sys.setenv(
  LEARNRTRACKR_DB = file.path(tempdir(), "learnrtrackr-course-pilot.sqlite"),
  LEARNRTRACKR_STUDENT_ID = "student_demo",
  LEARNRTRACKR_GROUP_ID = "A"
)

learnr::run_tutorial(
  file.path(example_dir, "tutorial.Rmd"),
  clean = TRUE,
  as_rstudio_job = FALSE
)
```

# Simulate a cohort

The example also includes a script that records simulated attempts for a small
cohort. This is useful for checking exports and reports without using the
browser.

```{r simulate, eval = FALSE}
source(file.path(example_dir, "simulate-results.R"))
```

# Inspect teacher outputs

After running the tutorial or the simulation:

```{r inspect, eval = FALSE}
source(file.path(example_dir, "inspect-results.R"))
```

The inspection script writes attempts, scores, gradebook rows, Moodle-ready
grades, a rich export bundle, and an HTML teacher report when `rmarkdown` is
available.

# Dashboard

The same database can be opened with the local teacher dashboard:

```{r dashboard, eval = FALSE}
run_dashboard(Sys.getenv("LEARNRTRACKR_DB"), group_id = "A")
```

The dashboard is a local inspection interface for prototypes. It does not
replace institutional authentication.

# Preflight checklist and protocol

The example includes `pilot-checklist.md` for operational checks and
`pilot-protocol.md` for a controlled pilot plan. Read both before using the
workflow with real learners.
