---
title: "Getting started with learnrTrackR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with learnrTrackR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`learnrTrackR` currently provides a small SQLite layer for simulated tutorial
attempts. It does not yet connect directly to `learnr` or `gradethis`.

## Create a database

```{r setup}
library(learnrTrackR)

db_path <- tempfile(fileext = ".sqlite")
con <- init_tracking_db(db_path, overwrite = TRUE)
```

## Register expected questions

Registered questions define the denominator used by `gradebook()`. In this
example, `q3` is expected but not answered.

```{r questions}
register_questions(
  con,
  tutorial_id = "module_01",
  questions = data.frame(
    question_id = c("q1", "q2", "q3"),
    max_score = c(1, 1, 1)
  )
)
```

## Add simulated attempts

```{r attempts}
track_attempt(
  con = con,
  student_id = "student_001",
  tutorial_id = "module_01",
  question_id = "q1",
  submitted_answer = "mean(x)",
  grade_status = "correct",
  score = 1,
  max_score = 1,
  feedback = "Correct."
)

track_attempt(
  con = con,
  student_id = "student_001",
  tutorial_id = "module_01",
  question_id = "q2",
  submitted_answer = "summarise(df, x = mean(x))",
  grade_status = "partial",
  score = 0.5,
  max_score = 1,
  feedback = "Good idea, but check grouping."
)
```

## Read attempts

```{r read-attempts}
get_attempts(con)
```

## Compute scores

`compute_scores()` summarizes only observed attempts.

```{r scores}
compute_scores(con, tutorial_id = "module_01", rule = "last")
```

`gradebook()` uses registered questions, so unanswered questions are included.

```{r gradebook}
gradebook(con, tutorial_id = "module_01", rule = "last")
```

## Export results

```{r export}
attempts_path <- tempfile(fileext = ".csv")
scores_path <- tempfile(fileext = ".csv")
gradebook_path <- tempfile(fileext = ".csv")

export_results(con, attempts_path, type = "attempts")
export_results(con, scores_path, type = "scores")
export_results(con, gradebook_path, type = "gradebook", tutorial_id = "module_01")

file.exists(c(attempts_path, scores_path, gradebook_path))
```

```{r cleanup, include = FALSE}
DBI::dbDisconnect(con)
```
