---
title: "Instructor adoption guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Instructor adoption guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Scope

This guide is written for an instructor who wants to try `learnrTrackR` in a
small, controlled teaching workflow. It focuses on adoption rather than package
development.

The current package supports a cautious prototype workflow:

1. prepare course, tutorial, student, and question metadata;
2. launch a tracked `learnr` tutorial;
3. store attempts in SQLite or PostgreSQL;
4. inspect teacher-facing results;
5. export Moodle-ready grades, Canvas Gradebook grades, and richer CSV bundles;
6. document privacy, retention, and known limitations.

This guide does not provide institutional authentication, Moodle API
integration, or a full production deployment plan.

# Start from the course pilot

The most complete example is the course pilot:

```{r locate}
library(learnrTrackR)

pilot_dir <- system.file("examples/course-pilot", package = "learnrTrackR")
pilot_dir
```

It contains the tutorial, simulated data, launch scripts, configuration files,
teacher outputs, an operational checklist, and a pilot protocol.

```{r list-files}
list.files(pilot_dir)
```

# Adoption workflow

## 1. Install and rehearse locally

Install the package from the local source tree or from GitHub. During package
development, from the repository root:

```{r install-local, eval = FALSE}
devtools::install(dependencies = FALSE)
```

Then rehearse the course pilot with simulated data:

```{r simulate, eval = FALSE}
source("inst/examples/course-pilot/simulate-results.R")
source("inst/examples/course-pilot/inspect-results.R")
```

This creates a local SQLite database and teacher-facing outputs without asking
learners to use the tutorial.

## 2. Adapt the configuration

Copy the course pilot configuration to a new working directory and edit the
CSV files:

```text
config-csv/
  courses.csv
  tutorials.csv
  students.csv
  questions.csv
```

The key adoption checks are:

1. every assessed question in the tutorial appears in `questions.csv`;
2. every expected learner appears once in `students.csv`;
3. the `student_id` values match the identifier that will be used for Moodle
   matching or teacher inspection;
4. `max_score` values match the intended grading scheme;
5. `group_id` values match the cohorts the teacher will inspect and export.

If a single-file configuration is easier to maintain, use the YAML template:

```{r yaml-template, eval = FALSE}
create_tracking_config_template("tracking.yml", format = "yaml")
```

## 3. Adapt the tutorial

For a new `learnr` tutorial, initialize tracking once in a setup chunk:

```{r setup-context, eval = FALSE}
tracking <- setup_learnr_tracking(
  db_path = Sys.getenv("LEARNRTRACKR_DB"),
  student_id = Sys.getenv("LEARNRTRACKR_STUDENT_ID"),
  config = "config-csv",
  require_registered_student = TRUE
)
```

Then use tracked question helpers for supported built-in question types:

```{r tracked-question, eval = FALSE}
tracked_question_radio(
  question_id = "q1",
  label = "Which value is the sample mean?",
  answer("6.42", correct = TRUE),
  answer("5.00"),
  tracking = tracking
)
```

For `gradethis` exercises, call `track_gradethis_attempt()` explicitly inside
the grading code.

## 4. Launch student and teacher scripts

For a student-style local launch:

```{sh student-launch, eval = FALSE}
cd inst/examples/course-pilot
cp student.env.example student.env
Rscript run-student.R
```

For teacher outputs:

```{sh teacher-launch, eval = FALSE}
cd inst/examples/course-pilot
cp teacher.env.example teacher.env
Rscript run-teacher.R
```

The teacher script creates attempts, scores, gradebook rows, Moodle-ready
grades, Canvas Gradebook grades, a rich export bundle, and an HTML teacher
report when `rmarkdown` is available.

## 5. Inspect before importing grades

Before importing into Moodle:

1. inspect the Moodle CSV manually;
2. confirm that the identifier column matches exactly one Moodle user per row;
3. confirm that any `group_id` filter excluded learners from other groups;
4. import first into a test activity or sandbox course when possible;
5. retain the generated CSV only as long as needed under the local data plan.

MoodleDocs documents CSV grade import through the Moodle gradebook. The
package deliberately exports CSV files and does not call the Moodle API.

Canvas also supports CSV uploads to the Gradebook. `export_canvas_grades()`
writes a Canvas Gradebook-style CSV, but the identifier columns must be
checked against the target Canvas course before import.

## 6. Choose the deployment boundary

SQLite is appropriate for local rehearsal and small prototypes. PostgreSQL is
the better rehearsal path when several learner sessions must write to the same
server-backed database.

For a local PostgreSQL rehearsal:

```{sh postgres-rehearsal, eval = FALSE}
cd inst/examples/postgres-docker
cp env.example .env
docker compose --env-file .env up -d
Rscript course-pilot-smoke-test.R
Rscript run-dashboard.R
```

The dashboard should be treated as a teacher inspection interface. It does not
replace institutional authentication or a managed access-control system.

# Pilot readiness gate

Before using the package with real learners, complete these checks:

- [ ] The tutorial version and question list are frozen for the pilot.
- [ ] The student identifier has been chosen and tested against Moodle.
- [ ] The database backend has been rehearsed from a clean start.
- [ ] The teacher export directory is outside Git and access-restricted.
- [ ] The Moodle CSV has been tested with a small sample.
- [ ] The dashboard, if used, is local or protected by the deployment
      environment.
- [ ] The data-retention period is documented.
- [ ] The instructor has read `pilot-checklist.md` and `pilot-protocol.md`.
- [ ] Research or publication claims have been separated from routine teaching
      use.

# What to record after the pilot

For software adoption and possible publication, record:

1. package version and Git commit;
2. database backend and deployment context;
3. tutorial identifier and version;
4. number of configured learners, without publishing direct identifiers;
5. number of attempts, missing submissions, and export issues;
6. teacher workflow problems observed during setup or grading;
7. data-retention decisions and any privacy deviations;
8. limitations that should be described in a paper or release note.

Do not claim learning gains, improved engagement, or reduced workload unless a
study design and collected data support those claims.

# References

- Posit Software, PBC. Accessed 2026-06-08. `learnr::run_tutorial()`.
  <https://pkgs.rstudio.com/learnr/reference/run_tutorial.html>
- MoodleDocs. Accessed 2026-06-08. Grade import.
  <https://docs.moodle.org/en/Grade_import>
- Posit Software, PBC. Accessed 2026-06-08. Posit Connect authentication.
  <https://docs.posit.co/connect/admin/authentication/>
- Interagency Advisory Panel on Research Ethics. 2022. TCPS 2: Ethical
  Conduct for Research Involving Humans.
  <https://ethics.gc.ca/eng/policy-politique_tcps2-eptc2_2022.html>
