---
title: "Using a learnr tracking context"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using a learnr tracking context}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Scope

This guide shows the recommended explicit `learnr` workflow for
`learnrTrackR`. The package does not intercept browser events or internal
`learnr` progress state. Instead, it creates a small tracking context in the
tutorial setup chunk and reuses that context in tracked questions and
`gradethis` checks.

The workflow is designed for local teaching prototypes and early course
experiments where the learner identifier is supplied by the tutorial launch
environment.

# Create the context

In a tutorial, the setup chunk should create one context and keep it available
to later question and check chunks.

```{r setup}
library(learnrTrackR)

db_path <- tempfile(fileext = ".sqlite")

tracking <- setup_learnr_tracking(
  tutorial_id = "module_01",
  student_id = "student_001",
  db_path = db_path,
  group_id = "A"
)

tracking
```

`setup_learnr_tracking()` initializes the SQLite database and registers the
current learner. Use `open_learnr_tracking_db()` when a chunk needs a database
connection.

```{r register-questions}
con <- open_learnr_tracking_db(tracking)

register_questions(
  con,
  tutorial_id = tracking$tutorial_id,
  questions = data.frame(
    question_id = c("q_radio", "q_code"),
    question_label = c("Mean multiple choice", "Mean code exercise"),
    question_type = c("radio", "code"),
    max_score = c(1, 1)
  )
)

get_students(con)
get_questions(con, tutorial_id = tracking$tutorial_id)

DBI::dbDisconnect(con)
```

# Track a learnr question

For built-in `learnr` questions, pass the context to `tracked_question()`.
This chunk is not evaluated in the vignette because `learnr` question
constructors must run inside a `learnr` tutorial document.

```{r question, eval = FALSE}
question <- tracked_question(
  "What is the mean of 2, 4, and 6?",
  learnr::answer("3"),
  learnr::answer("4", correct = TRUE, message = "Correct."),
  learnr::answer("6"),
  type = "radio",
  question_id = "q_radio",
  context = tracking,
  max_score = 1
)

learnr::question_is_correct(question, "4")
```

When `learnr` evaluates the answer in a running tutorial,
`learnrTrackR` records one attempt.

# Track a gradethis check

For code exercises, use `track_gradethis_attempt()` inside
`gradethis::grade_this()`. The key point is that the same `tracking` context can
replace repeated `con`, `student_id`, and `tutorial_id` arguments.

```{r gradethis-pattern, eval = FALSE}
gradethis::grade_this({
  correct <- isTRUE(all.equal(.result, mean(c(2, 4, 6))))
  feedback <- if (correct) {
    "Correct."
  } else {
    "Use mean(c(2, 4, 6))."
  }

  learnrTrackR::track_gradethis_attempt(
    context = tracking,
    question_id = "q_code",
    submitted_answer = .user_code,
    correct = correct,
    feedback = feedback,
    max_score = 1
  )
})
```

The same helper can be called directly in ordinary R code for testing.

```{r direct-gradethis}
track_gradethis_attempt(
  context = tracking,
  question_id = "q_code",
  submitted_answer = "mean(c(2, 4, 6))",
  correct = TRUE,
  feedback = "Correct.",
  max_score = 1
)
```

# Inspect the gradebook

```{r gradebook}
con <- open_learnr_tracking_db(tracking)

get_attempts(con)
gradebook(con, tutorial_id = tracking$tutorial_id, rule = "last")

DBI::dbDisconnect(con)
```

# Minimal setup chunk pattern

A real tutorial setup chunk usually reads `student_id`, `group_id`, and
`db_path` from environment variables:

```{r setup-pattern, eval = FALSE}
student_id <- learnrTrackR::get_tracking_student_id()
tutorial_id <- "module_01"

tracking <- learnrTrackR::setup_learnr_tracking(
  tutorial_id = tutorial_id,
  student_id = student_id,
  db_path = Sys.getenv("LEARNRTRACKR_DB"),
  group_id = Sys.getenv("LEARNRTRACKR_GROUP_ID", unset = NA_character_),
  config_path = "config"
)
```

The returned `tracking` object should then be passed to tracked questions and
code checks throughout the tutorial.
