---
title: "Exporting grades to Moodle"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exporting grades to Moodle}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Scope

This guide shows how to prepare a simple Moodle-ready CSV grade file from
`learnrTrackR`. The package does not call the Moodle API. The workflow is a
manual CSV import into the Moodle gradebook.

MoodleDocs states that grades can be imported as CSV or XML files, or by
pasting from a spreadsheet. MoodleDocs also notes that grade import is
equivalent to manual grading in the grader report, so imported grades should be
tested carefully before use in a real course.

# Create a small gradebook

```{r setup}
library(learnrTrackR)

db_path <- tempfile(fileext = ".sqlite")
con <- init_tracking_db(db_path, overwrite = TRUE)

register_students(
  con,
  data.frame(
    student_id = c("student_001", "student_002"),
    student_label = c("Student 1", "Student 2"),
    group_id = c("A", "A")
  )
)

register_questions(
  con,
  tutorial_id = "module_01",
  questions = data.frame(
    question_id = c("q1", "q2"),
    max_score = c(1, 1)
  )
)

track_attempt(
  con,
  student_id = "student_001",
  tutorial_id = "module_01",
  question_id = "q1",
  submitted_answer = "mean(x)",
  score = 1,
  max_score = 1,
  require_registered_student = TRUE
)

track_attempt(
  con,
  student_id = "student_002",
  tutorial_id = "module_01",
  question_id = "q1",
  submitted_answer = "sd(x)",
  score = 0,
  max_score = 1,
  require_registered_student = TRUE
)
```

# Build the Moodle table

`moodle_grades()` returns a wide table with one identifier column and one grade
column.

```{r moodle-table}
moodle_grades(
  con,
  tutorial_id = "module_01",
  grade_item = "Module 01 quiz"
)
```

By default, the identifier column is `useridnumber`, a common Moodle mapping
target when institutional student identifiers are stored in Moodle. If your
course uses a different field, change `id_column`.

```{r custom-id}
moodle_grades(
  con,
  tutorial_id = "module_01",
  id_column = "email",
  grade_item = "Module 01 quiz"
)
```

This example still uses `student_id` values in the exported `email` column,
because the example database does not store real email addresses. In a real
course, choose an identifier that matches exactly one Moodle user.

# Export the CSV file

```{r export}
csv_path <- tempfile(fileext = ".csv")

export_moodle_grades(
  con,
  path = csv_path,
  tutorial_id = "module_01",
  grade_item = "Module 01 quiz",
  grade_value = "percent",
  digits = 2
)

readr::read_csv(csv_path, show_col_types = FALSE)
```

Use `grade_value = "percent"` for a 0 to 100 grade, or `grade_value = "score"`
for the raw gradebook score.

# Suggested Moodle import workflow

Before importing into a real course:

1. Create the grade item in Moodle before importing.
2. Export a small gradebook sample from Moodle.
3. Confirm the user identifier field used in your course.
4. Generate a `learnrTrackR` CSV with the same identifier field.
5. Import the CSV in Moodle's gradebook import interface.
6. Preview the import and map the user field and grade item columns.
7. Validate the result on a small test group before importing a full cohort.

Do not add new grade columns in spreadsheet software after exporting from
Moodle. MoodleDocs warns that Moodle may reject imports containing columns that
did not exist in the exported gradebook. If a new grade item is needed, create
it in Moodle first.

# Privacy check before import

The Moodle grade CSV should contain only the identifier needed for matching and
the grade item column. Do not include attempts, feedback, free-text answers, or
pseudonymisation keys in a Moodle import file.

```{r disconnect, include = FALSE}
DBI::dbDisconnect(con)
```

# References

- MoodleDocs. Accessed 2026-06-04. Grade import.
  <https://docs.moodle.org/en/Grade_import>
- MoodleDocs. Accessed 2026-06-04. Capabilities/moodle/grade:import.
  <https://docs.moodle.org/en/Capabilities/moodle/grade%3Aimport>
- MoodleDocs. Accessed 2026-06-04. Capabilities/gradeimport/csv:view.
  <https://docs.moodle.org/en/Capabilities/gradeimport/csv%3Aview>
