---
title: "Controlled pilot deployment"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Controlled pilot deployment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Scope

This guide describes a controlled pilot deployment rehearsal for
`learnrTrackR`. It uses the simulated course pilot, PostgreSQL, environment
variables, teacher exports, Moodle-ready CSV output, dashboard data, and an
HTML teacher report.

The workflow is intended for development, local rehearsal, and small controlled
pilots. It is not an institutional authentication layer and it is not a
production LMS.

For the SQLite version of the same pilot, the `course-pilot` example includes
`run-student.R`, `run-teacher.R`, `student.env.example`,
`teacher.env.example`, and `pilot-checklist.md`.

# Example directories

```{r locate}
library(learnrTrackR)

postgres_dir <- system.file("examples/postgres-docker", package = "learnrTrackR")
course_pilot_dir <- system.file("examples/course-pilot", package = "learnrTrackR")

postgres_dir
course_pilot_dir
```

# Environment variables

The PostgreSQL Docker example includes an `env.example` file. Copy it to `.env`
before launching the service:

```{sh copy-env, eval = FALSE}
cp env.example .env
```

The important pilot variables are:

```text
LEARNRTRACKR_POSTGRES_DB=learnrtrackr
LEARNRTRACKR_POSTGRES_USER=learnrtrackr
LEARNRTRACKR_POSTGRES_PASSWORD=replace-with-a-long-random-password
LEARNRTRACKR_POSTGRES_HOST=127.0.0.1
LEARNRTRACKR_POSTGRES_PORT=5432
LEARNRTRACKR_POSTGRES_SCHEMA=learnrtrackr_pilot
LEARNRTRACKR_PILOT_TUTORIAL_ID=stat_descriptive_pilot
LEARNRTRACKR_PILOT_GROUP_ID=A
LEARNRTRACKR_PILOT_OUTPUT_DIR=pilot-outputs
LEARNRTRACKR_PILOT_RESET=true
LEARNRTRACKR_DASHBOARD_HOST=127.0.0.1
LEARNRTRACKR_DASHBOARD_TOKEN=replace-with-a-long-random-dashboard-token
```

Do not commit `.env` files, database dumps, or exported student results.

# Start PostgreSQL

From `inst/examples/postgres-docker/`:

```{sh start-postgres, eval = FALSE}
docker compose --env-file .env up -d
```

The Compose file starts one local PostgreSQL service. The pilot smoke test uses
the schema named by `LEARNRTRACKR_POSTGRES_SCHEMA`. When
`LEARNRTRACKR_PILOT_RESET=true`, that schema is dropped and recreated before
the simulated pilot is inserted.

# Run the pilot smoke test

```{sh smoke-test, eval = FALSE}
Rscript course-pilot-smoke-test.R
```

The smoke test:

1. connects to PostgreSQL;
2. prepares the pilot schema;
3. loads the course, tutorial, student, and question CSV configuration;
4. records the simulated cohort attempts;
5. prepares dashboard data with `dashboard_data(con, ...)`;
6. writes attempts, scores, gradebook, Moodle-ready grades, and a rich export
   bundle;
7. renders an HTML teacher report when `rmarkdown` is installed.

# Inspect the teacher outputs

By default, outputs are written to:

```text
inst/examples/postgres-docker/pilot-outputs/
```

Expected files include:

```text
course-pilot-attempts.csv
course-pilot-scores.csv
course-pilot-gradebook.csv
course-pilot-moodle.csv
course-pilot-teacher-report.html
course-pilot-bundle/
```

The Moodle CSV is filtered by `LEARNRTRACKR_PILOT_GROUP_ID`. For example,
`LEARNRTRACKR_PILOT_GROUP_ID=A` exports only the configured group A learners.

# Dashboard

The pilot verifies dashboard tables with:

```{r dashboard-data, eval = FALSE}
dashboard_data(
  con,
  tutorial_id = "stat_descriptive_pilot",
  group_id = "A",
  rule = "last"
)
```

The interactive dashboard can then be launched from the same PostgreSQL
environment:

```{sh run-dashboard-script, eval = FALSE}
Rscript run-dashboard.R
```

The script calls `run_dashboard_postgres()` with the configured PostgreSQL
schema, tutorial id, group filter, dashboard host, and dashboard token:

```{r run-dashboard-postgres, eval = FALSE}
run_dashboard_postgres(
  postgres_schema = Sys.getenv("LEARNRTRACKR_POSTGRES_SCHEMA"),
  tutorial_id = Sys.getenv("LEARNRTRACKR_PILOT_TUTORIAL_ID"),
  group_id = Sys.getenv("LEARNRTRACKR_PILOT_GROUP_ID"),
  host = Sys.getenv("LEARNRTRACKR_DASHBOARD_HOST", unset = "127.0.0.1"),
  access_token = Sys.getenv("LEARNRTRACKR_DASHBOARD_TOKEN")
)
```

# Teacher launch checklist

Before a real controlled pilot:

1. read `pilot-checklist.md` and `pilot-protocol.md` in the `course-pilot`
   example;
2. choose the student identifier used for Moodle matching;
3. prepare `students.csv` with only necessary student metadata;
4. set a PostgreSQL password that is not committed to Git;
5. use a dedicated PostgreSQL database or schema;
6. run `course-pilot-smoke-test.R`;
7. inspect `course-pilot-moodle.csv` before importing;
8. inspect the teacher report before using results for teaching decisions;
9. launch `run-dashboard.R` only from an explicitly managed local or protected
   environment;
10. document who can access exports and how long files are retained.

# Stop PostgreSQL

```{sh stop-postgres, eval = FALSE}
docker compose --env-file .env down
```

To delete the local data volume:

```{sh stop-postgres-volume, eval = FALSE}
docker compose --env-file .env down -v
```

# References

- PostgreSQL Global Development Group. Accessed 2026-06-04. libpq environment
  variables.
  <https://www.postgresql.org/docs/current/libpq-envars.htm>
- Docker Inc. Accessed 2026-06-04. Compose file reference.
  <https://docs.docker.com/compose/compose-file/>
- Docker Inc. Accessed 2026-06-04. postgres official image.
  <https://hub.docker.com/_/postgres>
