---
title: "Teacher workflow with learnrTrackR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Teacher workflow with learnrTrackR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette shows a minimal teacher workflow: declare course metadata,
tutorial metadata, students, and expected questions; record attempts; inspect
group-level results; and export CSV files.

## Create a configuration directory

```{r config}
library(learnrTrackR)

config_dir <- tempfile()
dir.create(config_dir)

readr::write_csv(
  data.frame(
    course_id = "stat101",
    course_label = "Statistics 101",
    semester = "W2026"
  ),
  file.path(config_dir, "courses.csv")
)

readr::write_csv(
  data.frame(
    tutorial_id = "module_01",
    course_id = "stat101",
    tutorial_label = "Module 1",
    version = "0.0.1"
  ),
  file.path(config_dir, "tutorials.csv")
)

readr::write_csv(
  data.frame(
    student_id = c("student_001", "student_002", "student_003"),
    student_label = c("Student 1", "Student 2", "Student 3"),
    group_id = c("A", "A", "B")
  ),
  file.path(config_dir, "students.csv")
)

readr::write_csv(
  data.frame(
    tutorial_id = "module_01",
    question_id = c("q1", "q2"),
    question_label = c("Mean exercise", "Summary exercise"),
    question_type = c("code", "code"),
    max_score = c(1, 1)
  ),
  file.path(config_dir, "questions.csv")
)
```

The same fields can also be represented in a YAML file and read with
`read_tracking_config()` when the `yaml` package is installed.

## Load the configuration

```{r load-config}
db_path <- tempfile(fileext = ".sqlite")
con <- init_tracking_db(db_path, overwrite = TRUE)

load_tracking_config(con, config_dir)
```

## Record attempts

```{r attempts}
track_attempt(
  con,
  student_id = "student_001",
  tutorial_id = "module_01",
  question_id = "q1",
  submitted_answer = "mean(x)",
  grade_status = "correct",
  score = 1,
  max_score = 1,
  require_registered_student = TRUE
)

track_attempt(
  con,
  student_id = "student_002",
  tutorial_id = "module_01",
  question_id = "q1",
  submitted_answer = "sd(x)",
  grade_status = "incorrect",
  score = 0,
  max_score = 1,
  require_registered_student = TRUE
)
```

## Inspect group results

```{r dashboard-data}
group_a <- dashboard_data(
  con,
  tutorial_id = "module_01",
  group_id = "A",
  rule = "last"
)

group_a$summary
group_a$students
group_a$gradebook
```

## Export teaching files

```{r export}
export_dir <- tempfile()
exported <- export_tracking_bundle(
  con,
  export_dir,
  tutorial_id = "module_01",
  group_id = "A",
  rule = "last"
)

exported
file.exists(exported$path)
```

The bundle contains summary, students, attempts, scores, gradebook, questions,
and Moodle-ready grade CSV files.

```{r cleanup, include = FALSE}
DBI::dbDisconnect(con)
```
