---
title: "Course pilot: descriptive statistics with R"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "A course-like learnr pilot using explicit learnrTrackR tracking, CSV configuration, and gradethis checks."
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(learnrTrackR)
library(dplyr)
library(tibble)

gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)

resolve_example_dir <- function() {
  env_dir <- Sys.getenv("LEARNRTRACKR_EXAMPLE_DIR", unset = "")
  if (nzchar(env_dir)) {
    return(env_dir)
  }

  installed_dir <- system.file("examples/course-pilot", package = "learnrTrackR")
  if (nzchar(installed_dir)) {
    return(installed_dir)
  }

  input <- knitr::current_input()
  if (!is.null(input) && nzchar(input)) {
    return(dirname(input))
  }

  "."
}

example_dir <- resolve_example_dir()
source(file.path(example_dir, "pilot-data.R"))

tutorial_id <- "stat_descriptive_pilot"
tracking_env <- learnrTrackR::get_learnr_tracking_env(
  default_db_path = file.path(tempdir(), "learnrtrackr-course-pilot.sqlite"),
  default_group_id = "A"
)

tracking <- learnrTrackR::setup_learnr_tracking(
  tutorial_id = tutorial_id,
  student_id = tracking_env$student_id,
  db_path = tracking_env$db_path,
  group_id = tracking_env$group_id,
  config_path = file.path(example_dir, "config-csv")
)

open_tracking_db <- function() {
  learnrTrackR::open_learnr_tracking_db(tracking)
}
```

## Identification

The tutorial reads the learner identifier, group, and database path from the
launch environment. For local testing, set `LEARNRTRACKR_STUDENT_ID`,
`LEARNRTRACKR_GROUP_ID`, and `LEARNRTRACKR_DB` before launching the tutorial.

```{r show-launch}
tibble::tibble(
  student_id = tracking$student_id,
  group_id = tracking$group_id,
  tutorial_id = tracking$tutorial_id,
  db_path = tracking$db_path
)
```

## Data

The data set is simulated. Each row represents one fictitious learner case from
a small course pilot.

```{r show-data}
pilot_survey
```

## Question 1

```{r q1_variable_type, echo=FALSE}
learnrTrackR::tracked_question(
  "Which variable is quantitative?",
  learnr::answer("learner_case"),
  learnr::answer("region"),
  learnr::answer("study_hours", correct = TRUE, message = "Correct."),
  learnr::answer("program"),
  type = "radio",
  allow_retry = TRUE,
  try_again = "Try again. Look for a variable measured on a numeric scale.",
  question_id = "q1_variable_type",
  context = tracking,
  max_score = 1
)
```

## Question 2

```{r q2_robust_summaries, echo=FALSE}
learnrTrackR::tracked_question(
  "Which summaries are usually robust to extreme values?",
  learnr::answer("Mean"),
  learnr::answer("Median", correct = TRUE),
  learnr::answer("Standard deviation"),
  learnr::answer("Interquartile range", correct = TRUE),
  type = "checkbox",
  allow_retry = TRUE,
  try_again = "Try again. Robust summaries should not change too much when one value is extreme.",
  question_id = "q2_robust_summaries",
  context = tracking,
  max_score = 1
)
```

## Question 3

```{r q3_n_rows, echo=FALSE}
learnrTrackR::tracked_question(
  "How many rows are in the pilot data set?",
  learnr::answer(12, correct = TRUE, message = "Correct."),
  type = "numeric",
  allow_retry = TRUE,
  min = 0,
  max = 30,
  step = 1,
  question_id = "q3_n_rows",
  context = tracking,
  max_score = 1
)
```

## Question 4

```{r q4_highest_median, echo=FALSE}
learnrTrackR::tracked_question(
  "Which region has the highest median study_hours value?",
  learnr::answer_fn(
    function(value) {
      answer <- tolower(trimws(value))
      if (answer == "sherbrooke") {
        learnr::correct("Correct. Sherbrooke has the highest median study_hours value.")
      } else {
        learnr::incorrect("Try again. Compute the median study_hours value by region.")
      }
    },
    label = "highest median checker"
  ),
  type = "text",
  allow_retry = TRUE,
  question_id = "q4_highest_median",
  context = tracking,
  max_score = 1
)
```

## Code exercise 1

Compute the mean of `study_hours`.

```{r q5_mean_study_hours, exercise=TRUE}
mean(pilot_survey$study_hours)
```

```{r q5_mean_study_hours-solution}
mean(pilot_survey$study_hours)
```

```{r q5_mean_study_hours-check}
gradethis::grade_this({
  expected <- mean(pilot_survey$study_hours)
  correct <- is.numeric(.result) && isTRUE(all.equal(.result, expected))
  feedback <- if (correct) {
    "Correct. This is the mean study time across all rows."
  } else {
    "Try again. Use mean(pilot_survey$study_hours)."
  }

  learnrTrackR::track_gradethis_attempt(
    context = tracking,
    question_id = "q5_mean_study_hours",
    submitted_answer = .user_code,
    correct = correct,
    feedback = feedback,
    max_score = 1
  )
})
```

## Code exercise 2

Create one row per region with:

- `region`
- `n`
- `median_study_hours`
- `mean_quiz_score`

```{r q6_region_summary, exercise=TRUE}
pilot_survey |>
  group_by(region) |>
  summarise(
    n = n(),
    median_study_hours = median(study_hours),
    mean_quiz_score = mean(quiz_score),
    .groups = "drop"
  )
```

```{r q6_region_summary-solution}
pilot_survey |>
  group_by(region) |>
  summarise(
    n = n(),
    median_study_hours = median(study_hours),
    mean_quiz_score = mean(quiz_score),
    .groups = "drop"
  )
```

```{r q6_region_summary-check}
gradethis::grade_this({
  expected <- pilot_survey |>
    dplyr::group_by(region) |>
    dplyr::summarise(
      n = dplyr::n(),
      median_study_hours = median(study_hours),
      mean_quiz_score = mean(quiz_score),
      .groups = "drop"
    ) |>
    dplyr::arrange(region)

  candidate <- tryCatch(
    {
      .result |>
        as.data.frame() |>
        dplyr::arrange(region)
    },
    error = function(cnd) NULL
  )

  required_columns <- c("region", "n", "median_study_hours", "mean_quiz_score")
  has_required_columns <- !is.null(candidate) &&
    all(required_columns %in% names(candidate))

  correct <- has_required_columns &&
    nrow(candidate) == nrow(expected) &&
    isTRUE(all.equal(candidate$n, expected$n)) &&
    isTRUE(all.equal(candidate$median_study_hours, expected$median_study_hours)) &&
    isTRUE(all.equal(candidate$mean_quiz_score, expected$mean_quiz_score))

  score <- if (correct) {
    2
  } else if (has_required_columns) {
    1
  } else {
    0
  }

  grade_status <- if (correct) {
    "correct"
  } else if (score > 0) {
    "partial"
  } else {
    "incorrect"
  }

  feedback <- if (correct) {
    "Correct. The grouped summary matches the expected result."
  } else if (has_required_columns) {
    "Partial credit. The expected columns are present, but at least one value differs."
  } else {
    "Try again. Create the columns region, n, median_study_hours, and mean_quiz_score."
  }

  learnrTrackR::track_gradethis_attempt(
    context = tracking,
    question_id = "q6_region_summary",
    submitted_answer = .user_code,
    correct = correct,
    score = score,
    max_score = 2,
    grade_status = grade_status,
    feedback = feedback
  )
})
```

## Teacher outputs

After learner attempts have been recorded, use `inspect-results.R` in this
example directory to create attempts, scores, gradebook, Moodle, bundle, and
teacher report outputs.
